%  Preface and permission of use on load

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Preface}
\noindent \textbf{\huge Preface}

\vspace{1.5cm}

\noindent
``The author gives permission to make this master dissertation available for consultation and to copy parts
of this master dissertation for personal use. In all cases of other use, the copyright terms have to be respected,
in particular with regard to the obligation to state explicitly the source when quoting results from this master
dissertation.''

\vspace{1cm}

\noindent Sitt Min Oo, May 23, 2021 


\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgement}
\noindent \textbf{\huge Acknowledgement}

\vspace{1.5cm}
First, I would like to thank Anastasia Dimou for offering the opportunity to 
work with IDLab for the past summers. This provided me a lot of experience 
in working with Semantic Web technologies which were vital for this 
thesis. Furthermore, I would like to extend my gratitude to Ruben Verborgh 
for inspiring me to further specialize in the field of Semantic Web and for giving amazing 
lectures in Web Development where it all started. I would also like to thank Gerald Haesendonck for 
his continuous guidance and great feedback on the thesis throughout the course of this semester. 
Clearly, it would have been a much more difficult journey for me, without the guidance from your 
respective area of expertise.

Nevertheless, I would also like to thank the great friends I have made throughout my education 
at Ghent University. Dries, without you coming up for the first conversation during my freshman's year, I would 
have missed making a great friend for life. You and Arne are the best friends I could have for every single 
event, moment, and project we could do together! Kobe, Tibo, Jonathan, and Arthur, without your company,  
my days would have been spent silently working alone. 
A huge thanks to all of you guys for being the amazing friends that you all are!  

Lastly, all of this would have been impossible, if not for my parents dedicating a significant part of 
their life to make it here. Thank you mom and dad for not giving up even when life was really difficult 
for you. 
I thank you both deeply from my heart for being there when I was at my lowest and guiding me to become 
who I am today. 

\vspace{1cm}
\noindent Sitt Min Oo, May 23, 2021 
