\chapter{Methodology}%
\label{chap:Methodology}


In this chapter, we introduce a dynamic approach to windowing in data stream processing 
with the following improvements to fixed size window; 
\begin{enumerate*}[label=(\alph*)]
    \item stream-characteristic-aware processing 
    \item adaptive window sizes, and 
    \item high throughput with low latency processing. 
\end{enumerate*}

Existing fixed size windows are inflexible when the characteristics of a data stream,  
such as the stream rate, changes over time. Either the window size is 
too small to produce any output or too large which leads to high memory usage when 
the stream rate is high. Furthermore, fixed size windows only process the 
records inside the window at fixed interval (usually equals to the size of the window). 
This leads to high latency. Solving these disadvantages leads us to our approach 
of a dynamic window, which could readjusts its size during runtime,
for low latency and high throughput solution. 


\TODO{Chapter outline}



\section{Analysis for the implementation site}
\label{sec:analysis implementation site}
There are two possible site to implement our dynamic window; 
near the input data source, and as the final operation right before 
emitting RDF triples.  


\section{Operator inside window}
\label{sec:Operator inside window}
Which type of operation is suitable for our dynamic window? 
In the context of this work with RMLStreamer, we will have to consider optimizing the 
\emph{join} operation over \emph{aggregation}. 

RDF mapping engines focus 
on just mapping the input to RDF compliant formats without 
applying complex stream processing queries like \emph{aggregations} and 
\emph{reductions}. These stream processing queries, if required, could be 
delegated to the RDF stream processing frameworks processing RDF data streams.

Therefore, we focus on a reference implementation of dynamic windows with 
stream joins as part of the mapping process of non-heterogeneous data streams 
to RDF data streams. 
\section{Dynamic Window}%
\label{sec:Dynamic Window}

A dynamic window is a type of partitioned window (Chapter~\ref{sec:Partitioned Window}).
It first groups the incoming streams into keys 



