

\chapter{Semantic Web Technologies}
Multiple framework exists to deal with c
This section will define and describe the different notations and terms used throughput
the rest of this work. We will elaborate more on RDF, RML and stream windowing for more
intuition behind the approach of this work.


\section{RDF}
Resource Definition Framework \cite{rdf_concepts} is a framework for representing data on the Web.
It portrays the data as a directed graph with the resources as nodes in the graph and the
edges as the relationship between the different resources.
Figure~\ref{fig:rdf_triple_ex} shows an example of an RDF triple statement describing
the information “John has an apple”.
The triple statement consists of the subject \textit{John}, the predicate \textit{has}
and the object \textit{apple}.

\begin{figure}[htbp]
    \centering
    \begin{tikzpicture}[node distance={30mm}, main/.style = {draw, circle}]

        \node[main] (subject) {John};
        \node[main] (object) [right of=subject] {apple};

        \draw[->, thick] (subject) -- node[midway, above, sloped] {has} (object);

    \end{tikzpicture}
    \caption{An RDF triple representing the information “John has an apple”.}

    \label{fig:rdf_triple_ex}
\end{figure}


By composing these simple triple statements into a set of RDF triples, it yields us an RDF graph.
In Figure~\ref{fig:rdf_graph_ex}, 4 triple statements are composed together to form a
simple RDF graph describing \textit{John} and \textit{Mary} having the same \textit{apple}.
It might not be evident from the simple figures, about the advantages of
RDF graphs. Data representation in a graph model allows machines to follow the
\textit{links} between the resources, and discover more unknown
data in the linked knowledge graph. Link following is possible due to the nodes in
the triples being classified as one of the 3 different term types.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[node distance={45mm}, main/.style = {draw, circle}]

\node[main] (subject) {John};
\node[main] (subject_2) [below of=subject] {Mary};
\node[main] (object) [right of=subject] {apple};
\node[main] (apple_object_colour) [above right of=object] {red};
\node[main] (apple_object_ripe) [below right of=object, text width=15mm] {Malus domestica};
\node [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em]
(colour_kg) [below right of=apple_object_colour] {colours KG};

\draw[->, thick] (subject) -- node[midway, above, sloped] {has} (object);
\draw[->, thick] (subject_2) -- node[midway, above, sloped] {has} (object);
\draw[->, thick] (apple_object_colour) -- (colour_kg);
\draw[->, thick] (object) -- node[midway, above, sloped] {has colour} (apple_object_colour);
\draw[->, thick] (object) -- node[midway, above, sloped] {scientific name} (apple_object_ripe);
\end{tikzpicture}
\caption{A simple RDF graph where the same “apple” is shared by both John and Mary.}
\label{fig:rdf_graph_ex}
\end{figure}

\subsection{Term types}
Resources are classified into 3 different term types; IRI (Internationalized Resource Identifier),
literals and blank nodes. IRI is a string identifier unique in the global scope to
represent a resource. It is usually in the form of a web address, however, it can
also be in other forms so long as it conforms to the syntax defined in
RFC 3987~\footnote{RFC 3987: \url{https://www.ietf.org/rfc/rfc3987.txt}}.
IRI can represent a relationship, a concept or an object. Therefore, it could be
used in the \textit{subject}, the \textit{predicate} and the \textit{object} components of
an RDF triple.

Literals term type is used to represent a value such as strings, numbers, boolean and dates.
To ensure that the machines know the type of the data being read, we could
explicitly specify the type of the data with a datatype IRI. Moreover, the
language in which the data is written, could also be explicitly stated with
a language tag.

Lastly, we have the term type blank nodes. Blank nodes identify resources
in the local scope (i.e. to a local file or an RDF store). Since it is used to
identify resources in nodes, blank nodes are only applicable as the \textit{subject}
and the \textit{object} components of an RDF triple.


\subsection{TURTLE syntax}
The aforementioned term types are defined for abstract RDF syntax. For a concrete syntax to write
RDF triples, we would focus on the TURTLE (Terse RDF Triple Language)~\cite{turtle_syntax}
syntax in this work. A simple triple statement is a sequence of
\textit{subject, predicate, object} terms, ending in a '.'.
To reduce the repetition of writing the same subject and predicate combination with
different objects, TURTLE allows the use of ',' to separate the different objects.
Additionally, one could also use ';' to separate the different predicates and objects sharing the
same subject. 


\begin{lstlisting}[label={lst:same_subject}, 
    caption={Usage of ';' where triples share the same subject.}]
<http://example.org/apple>  <http://example.org/hasColor> "red";
                            <http://example.org/scientificName> "Malus domestica".
\end{lstlisting}

\begin{lstlisting}[label={lst:different_object}, 
    caption={Usage of ',' where triples differs only in the objects.}]
<http://example.org/apple>  <http://example.org/scientificName> "Malus pumila", 
                                                                "Malus domestica".
\end{lstlisting}


IRIs are written between the angle brackets like \lstinline{<http://example.org/#John>}.
Since blank nodes are locally scoped version of IRIs, the same syntax to write IRIs is also used.
TURTLE syntax allows us to define \textit{prefixes} at the head of the TURTLE file.
Users could then use prefixes, to write RDF triples in a more compact form. For example,
\lstinline{<http://example.org/#John>} could be shortened to
\lstinline{<#John>} using the relative \textit{@base} path.

\begin{lstlisting}[caption=Prefixes in TURTLE syntax.]
    @base <http://example.org/> . # default base IRI
    @prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#> .
    @prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#> .
    @prefix foaf: <http://xmlns.com/foaf/0.1/> .
    @prefix rel: <http://www.perceive.net/schemas/relationship/> . 
    ... 
\end{lstlisting}

Literals are written between the double quote '"'. It has a default datatype of 
a string. One could also \textit{cast} the literal value to a specific datatype 
by appending '\textasciicircum{} \textasciicircum{} $[$IRI of the datatype$]$'. For example, 
"12" is cast to an integer in \lstinline{"12"^^xsd:integer}. Language of the literal value 
could also be specified using \textit{@} similarly to datatype casting. 


\section{RML}
RDF Mapping Language\cite{rml} is a superset of the W3C's R2RML\cite{r2rml} which maps relational databases to
RDF datasets. RML improves upon R2RML by expressing mapping rules from heterogeneous
data sources and transforming them to RDF datasets whereas R2RML could only consume
data from relational databases. RML mapping file is composed of one or more \emph{triples maps}, 
which in turn consist of \emph{subject, predicate} and \emph{object} term maps. As the names imply, 
the term maps are used to map elements of the data sources to their respective terms 
in an RDF triple. The definitions of these maps are similar to the 
specifications in R2RML\cite{rml_tech}. 

Logical sources could be defined by specifying the \emph{source, logical iterator} 
and zero or one \emph{reference formulation} property. The logical sources in the default 
RML mapping file are bounded data, where the data already exists and has a predetermined
size. RMLStreamer extends the vocabulary of RML to also handle unbounded data in 
a streaming context. 

RML supports defining relationships amongst the different 
logical sources through the use of \textit{rr:parentTriplesMap, rr:joinCondition, rr:child and rr:parent}
properties. The relationship definitions are


\begin{lstlisting}[caption=An example of a RML mapping file.]
    
    
\end{lstlisting}
