\section{INTRODUCTION}
\label{chap:intro}

%Heterogeneous data formats, such as CSV or HTML, are not
%designed to semantically enrich the data they represent and 
%machines have difficulty interpreting these data automatically.
Various data formats such as CSV or HTML are not designed to contain the semantics of their data
which avoids machines to automatically interpret these data. 
To ensure that these heterogeneous data format are interpretable and 
processable by machines, data formats based on W3C standards, such as Resource Description 
Framework (RDF) triples~\cite{intro_rdf}, are developed. 
There exist state-of-the-art approaches to consolidate heterogeneous data
and transform them to an RDF serialization in a streaming environment. 

These approaches support traditional stream operators like joins and aggregations. 
However, they do not consider
the characteristics of streaming data sources such as velocity and 
time-correlations between the different
input streams, either due to the 
fixed size windows or custom solutions which they apply. 

Therefore, we propose a dynamic window as a solution to varying characteristics of streaming data. We evaluated our 
approach with the join operator applied inside the window. 
The dynamic window improves the performance of the 
join operator with higher throughput, lower latency and 
similar memory usage compared to a fixed size window.

The source code and the evaluation setup code can be found at
\url{https://github.com/RMLio/RMLStreamer/tree/feature/window_joins}, and 

\href{https://github.com/Kortika/Thesis-test-scripts.git}{https://github.com/Kortika/Thesis-test-scripts.git} respectively.
