\section{DYNAMIC WINDOW}%
\label{sec:Dynamic Window}
A dynamic window is a type of partitioned window~\cite{generic_window_sem}.
We define it as a group of subwindows, which update their sizes dynamically according to the characteristics 
of the data stream. It groups the incoming streams into different partitions first, according to 
the \emph{key} attribute value of the records. Subsequently, these grouped records are assigned 
to individual subwindows. These subwindows adjust their own size independently from each other 
at each update cycle. Furthermore, the subwindows will be independent from each other such 
that the stream rate is local to the attribute value for which each subwindow is responsible. 

\subsection{Dynamic window join}
\label{sub:Dynamic window join}

The join algorithm used, is a variant of Symmetric Hash Join~\cite{symmetric_hash_join}. 
The subwindows themselves work like a hash table, containing records with a 
specific \emph{key} --- since they are \emph{partitioned}. 
The records are joined by probing the relevant stream and generating the 
joined result. 


\subsection{Dynamic window algorithm}%
\label{sub:Dynamic window algorithm}
For each subwindow, the following configuration parameters 
are provided: 

\begin{itemize}
    \item $\Delta n$: the \textbf{initial} interval of time before the next eviction trigger. 
    \item $\epsilon_u$: the upper limit for threshold $\epsilon$.
    [GH: what kind of threshold? Specify somewhere that  the $\epsilon$s define thresholds for cost.]
    \item $\epsilon_l$: the lower limit for threshold $\epsilon$. 
    \item $U$: the upper limit for the window size. 
    \item $L$: the lower limit for the window size. 
\end{itemize}

Since we are implementing the join operator, the trigger event is fired when current record 
$r_c$ arrives, and the symmetric hash join is executed. We denote the current window as 
$W$ with the size as $|W|$. The streams are denoted as $S_P$ and $S_C$ with 
the corresponding states $List_P$ and $List_C$, for the parent and 
the child stream respectively. The states contain the records from their 
respective streams inside the subwindows.

The eviction trigger is fired every time when the current watermark 
$w \ge |W| + \Delta n$. At each eviction trigger we calculate
the cost for each \emph{list states} $List_P$ and $List_C$, containing the records from $S_P$ and $S_C$
respectively. The cost for $cost(List_P) = |S_P|/Size(List_P)$, idem for $cost(List_C)$. 
The total cost is $m = cost(List_P) + cost(List_C)$ and it is checked against thresholds $\epsilon_l$ and $\epsilon_u$. If  $\epsilon_l \le m \le \epsilon_u$, 
$\Delta n$ stays the same, otherwise it will be adjusted accordingly. This provides some stability 
in window size by keeping the same size if the cost lies within the thresholds. 
The higher $m$, the higher the stream rate. Thus, the subwindow needs to be frequently 
evicted and lower $\Delta n$ to reduce memory usage. There is also a limit on the 
minimum and maximum window sizes, $L$ and $U$ respectively, to ensure that the window 
size $\Delta n$ does not keep growing or shrinking in size infinitely in a worst-case scenario. 
The sizes of the list states 
are also updated according to $Size(List_P) = Size(List_P) * cost(List_P) + 0.5$.
Similarly for $Size(List_C)$. 
Hence the dynamic window maintains an 
ideal size by adjusting $\Delta n, Size(List_P)$ and $Size(List_C)$ according to 
the stream rate. The pseudo code for the eviction algorithm is presented in Algorithm~\ref{alg:dynamic_eviction}.

This algorithm for the dynamic window is an adaptation of the VC-TWindow~\cite{vctw_join} with 
improvements for stability in window sizing, clarity in the metrics used for updates, and localization 
of window size update to each subwindow.  

\begin{algorithm}[htbp]
    \DontPrintSemicolon
    \KwData{$\Delta n, \epsilon_u, \epsilon_l, U, L, List_P, List_C, S_P, S_C$}

    $cost(List_P) = |S_P| / Size(List_P)$      
    
    $cost(List_C) = |S_C| / Size(List_C)$     


    total cost $ m = cost(List_P) + cost(List_C)$  
  
    \If{$m > \epsilon_u$} 
    {
    
        $\Delta n = \Delta n / 2 $ 
        
        $Size(List_P) = Size(List_P) * (cost(List_P) + 0.5)$  

        $Size(List_C) = Size(List_C) * (cost(List_C) + 0.5)$  
    }
    \ElseIf{$m < \epsilon_l$}
    {
   
        $\Delta n = \Delta n * 2$ 

        $Size(List_P) = Size(List_P) * (cost(List_P) + 0.5)$  

        $Size(List_C) = Size(List_C) * (cost(List_C) + 0.5)$  
    }

    clean both $List_C \text{ and } List_P$
    \caption{Dynamic window $onEviction$ routine}
    \label{alg:dynamic_eviction}
\end{algorithm}



